On particular examples of planar integral point sets and their classification \footnote{ This work was carried out at Voronezh State University and supported by the Russian Science Foundation grant 19-11-00197. }

### 2021-02-24 AvdMomZvolA_examples/ips_examples.tex
[AMZAE] Intro is almost done

While the minimal possible diameter for planar integral point sets of given cardinality was being counted,
it was noticed~\cite{kurz2008minimum} that such diameter is attained at sets with many points on a straight line;
for some estimations on this tendency, we also refer the reader to~\cite{solymosi2003note}.

@@

It's notable that any of the examples that are discussed below
is located on a union of at most three straight lines.
In the most pictures these lines are shown as solid lines.
For classification of planar IPS that are located on a union of two straight lines,
we refer the reader to~\cite{avdeev2019particular}.

There are some examples of planar IPS that are not contained in the union of any three straight lines:
for examples, these are heptagons presented in~\cite{kreisel2008heptagon} and 7-clusters from~\cite{kurz2013constructing}.
However, we have to keep in mind that the circular inversion under certain conditions
translates an integral point set into an integral point set
(although sometimes additional dilation is necessary).
On the other hand, the circular inversion may translate a straight line into a circle and vice versa.

Thus, we can consider \emph{generalized circles}, that are circles or straight lines;
obviously, in that point of view all the examples from~\cite{kreisel2008heptagon} and~\cite{kurz2013constructing}
are located on a union of three generalized circles,
because each seven points are located on a union of a circle and two straight lines.

>>>>

While the minimal possible diameter for planar integral point sets of given cardinality was being computed,
it was noticed~\cite{kurz2008minimum} that such diameter is attained at sets with many points on a straight line;
for some estimations on this tendency, we also refer the reader to~\cite{solymosi2003note}.
Thus, the following classification was introduced:
\begin{dfn}
	A planar integral point set $M$ is said to be in \emph{semi-general position}
	if no three points of $M$ are located in a straight line.
\end{dfn}

The most dominating examples of PIPS in semi-general position are circular sets.
\begin{dfn}
	A planar integral point sets that is situated on a circle is said to be a \textit{circular}
	point set.
\end{dfn}

So, the following constraint appeared.
\begin{dfn}
	A planar integral point set $M$ is said to be in \emph{general position}
	if no three points of $M$ are located in a straight line
	and no four points of $M$ are located in a circle.
\end{dfn}

Planar integral point sets in general position are very difficult to find;
the first known examples were presented in~\cite{kreisel2008heptagon}.
As for now, there is no known example of PIPS of cardinality 8 in general position.

@@

It's notable that any of the examples that are discussed below
is located on a union of at most three straight lines.
%In the most pictures these lines are shown as solid lines.
For classification of planar IPS that are located on a union of two straight lines,
we refer the reader to~\cite{avdeev2019particular}.

There are some examples of planar IPS that are not contained in the union of any three straight lines:
for examples, these are heptagons presented in~\cite{kreisel2008heptagon} and 7-clusters from~\cite{kurz2013constructing}.
However, we have to keep in mind that the circular inversion under certain conditions
translates an integral point set into an integral point set
(although sometimes additional dilation is necessary).
On the other hand, the circular inversion may translate a straight line into a circle and vice versa.
Thus, we can consider \emph{generalized circles}, that are circles or straight lines;
obviously, in that point of view all the examples from~\cite{kreisel2008heptagon} and~\cite{kurz2013constructing}
are located on a union of three generalized circles,
because each seven points are located on a union of a circle and two straight lines.
